Hierarchical Control for Aircraft Electronic Power Systems

### 2012-12-08 project/report/paper.tex
priority table for example 2

%\begin{table}[t]
%\caption{Optimizing LMS reduces load shedding compared to the LL-LMS load shedding policy.}
%\label{T:example-1}
%\centering
\begin{tabular}{c|cc}
Sheddable loads (W) & Shed priority \\ \hline
60,000 & 1 (least preferred to shed) \\
60,000 & 2 (middle priority to shed) \\ 
40,000 & 3 (most preferred to shed) \\ \hline
\end{tabular}
%\end{table}

@@

Timestep 1 (live data matches historical data):
    Load Shedding Priority Table:
    Load 1: 40,000W, least preferred to shed.
    Load 2: 40,000W, second-least preferred to shed
    Load 3: 20,000W, most preferred to shed

Timestep 2 (historical data):
    Load Shedding Priority Table:
    Load 1: 40,000W, least preferred to shed.
    Load 2: 40,000W, second-least preferred to shed
    Load 3: 20,000W, most preferred to shed

Timestep 2 (live data):
    Load Shedding Priority Table:
    Load 1: 20,000W, least preferred to shed.
    Load 2: 40,000W, second-least preferred to shed
    Load 3: 40,000W, most preferred to shed

>>>>

\begin{tabular}{c|cc}
Sheddable loads (W) & Shed priority \\ \hline
60,000 & 1 (least preferred to shed) \\
60,000 & 2 (middle priority to shed) \\ 
40,000 & 3 (most preferred to shed) \\ \hline
\end{tabular}

@@

Timestep 1 (live data matches historical data):\\
\begin{tabular}{c|cc}
Sheddable loads (W) & Shed priority \\ \hline
40,000 & 1 (least preferred to shed) \\
40,000 & 2 (middle priority to shed) \\ 
{\bf 20,000} & 3 (most preferred to shed) \\ \hline
\end{tabular}

Timestep 2 (historical data): \\
\begin{tabular}{c|cc}
Sheddable loads (W) & Shed priority \\ \hline
40,000 & 1 (least preferred to shed) \\
40,000 & 2 (middle priority to shed) \\ 
{\bf 20,000} & 3 (most preferred to shed) \\ \hline
\end{tabular}

Timestep 2 (live data): \\
\begin{tabular}{c|cc}
Sheddable loads (W) & Shed priority \\ \hline
40,000 & 1 (least preferred to shed) \\
40,000 & 2 (middle priority to shed) \\ 
{\bf 40,000} & 3 (most preferred to shed) \\ \hline
\end{tabular}
